### 2013-08-22 notation.tex
Two more figures.

%----------------------------------------------------------------------
\section{Base implementation}
We present an implementation written in C++ for the case of 4 matrices and 4 vectors to run on the host system and serve as base of comparison against more optimized code written with register based routines optimized for the MIC. Such an implementation is as follows:
\begin{verbatim}
\end{verbatim}
%----------------------------------------------------------------------
\section{Floating point operations}
We compute the floating point operations of the SpMV with general $n_v$ and $n_m$. Calling the total number of floating point operations $N_F$, we find
$$
  N_F = 2 n_r n_z n_v m_m
$$
Thus the number of flpos to bytes transferred is $N_F / (n_{rT} + n_{wT})$, which when written out, 
\begin{eqnarray}
N_F &=& \frac{2 n_r n_z n_v n_m}{b_x n_r n_v  + n_r n_z b_i + n_r n_m n_z b_x + n_r n_m n_v b_x} \nonb \\
N_F &=& \frac{2 n_z n_v n_m}{b_x ( n_v + n_m n_z + n_m n_v) + n_z b_i}  \nonb \\
%N_F &=& \frac{2 n_r n_z n_v n_m}{b_x n_r n_v (n_v+n_m) + n_r n_z b_i + n_r n_m n_z b_x} \nonb \\
    %&=& \frac{2 n_z n_v n_m}{b_x (n_v+n_m) + n_z (b_i + n_m b_x)} \nonb 
\end{eqnarray}
In the special case $n_v=n_m=1$, 
$$
N_F = \frac{2 n_z}{n_z b_i + (n_z +2) b_x}
$$
Neglecting $2$ compared to $n_z$, we find that $N_F = 2/(b_i+b_x)$, which leads to 
$N_F = 2/8=1/4$ and  $N_F=2/12=1/6$ for single and double precision, respectively. 
In the general case, in the condition of $n_z$ large compared to 2, 
$$
N_F =  \frac{2 n_v n_m}{n_m b_x + b_i}
$$ 
The case are interested in is $n_m=n_v=4$, so that
$$
N_F = \frac{8}{ b_x + 1}
$$
which is 8/5 and 8/9 in single and double precision, respectively. 
In single and double precision, we get $N_F=32/36=8/5$ and $N_F=32/68=8/9$, respectively.
The third column of the following table (TABLE ???) is the maximum achievable Gflop rate, assuming 
a maximum memory transfer speed of $150 Gflops$ (see earlier benchmark in this paper). 
(higher speeds can be achieved in practice,  upwards of 190 Gflops (Saule \etal\cite{}), but we use
a benchmark code similar to our current algorithm, without the indirect acessing required for $x$, but keeping the same use of vector registers used in our fastest implementation. (DO WE INCLUDE the CODE?)

>>>>

%----------------------------------------------------------------------
\section{Base implementation}
We present an implementation written in C++ for the case of 4 matrices and 4 vectors to run on the host system and serve as base of comparison against more optimized code written with register based routines optimized for the MIC. Such an implementation is as follows:
\begin{verbatim}
\end{verbatim}
%----------------------------------------------------------------------
\section{Floating point operations}
We compute the floating point operations of the SpMV with general $n_v$ and $n_m$. Calling the total number of floating point operations $N_F$, we find
$$
  N_F = 2 n_r n_z n_v m_m
$$
Two cases must be distinguished in regards to $x$. In the first, in a worst case scenario, each element 
of $x$ is transferred $n_z$ times from memory. In the best case, the case of infinite cache, each element is transferred only once. Thus, we provide best and worst case scenarios and will compare against matrices $A$
in each of these extreme situations to evaluate the degree we approach idea performance. 
Thus the number of flops to bytes transferred is $N_F / (n_{rT} + n_{wT})$, which when written out, 
\begin{eqnarray}
N_{Fw} &=& \frac{2 n_r n_z n_v n_m}{b_x n_r n_z n_v  + n_r n_z b_i + n_r n_m n_z b_x + n_r n_m n_v b_x} \nonb \\
    &=& \frac{2 n_v n_m}{b_x ( n_v + n_m + n_m n_v n_z^{-1}) + b_i}  \nonb \\
%N_F &=& \frac{2 n_r n_z n_v n_m}{b_x n_r n_v (n_v+n_m) + n_r n_z b_i + n_r n_m n_z b_x} \nonb \\
    %&=& \frac{2 n_z n_v n_m}{b_x (n_v+n_m) + n_z (b_i + n_m b_x)} \nonb 
\end{eqnarray}
while in the best case, 
\begin{eqnarray}
N_{Fb} &=& \frac{2 n_r n_z n_v n_m}{b_x n_r n_v  + n_r n_z b_i + n_r n_m n_z b_x + n_r n_m n_v b_x} \nonb \\
    &=& \frac{2 n_v n_m}{b_x ( n_v n_z^{-1} + n_m  + n_m n_v n_z^{-1}) + b_i } 
\end{eqnarray}
In the special case $n_v=n_m=1$, 
$$
N_{Fw} = \frac{2}{b_x (2+n_z^{-1}) + b_i}
$$
and 
$$
N_{Fb} = \frac{2}{b_x (1 + 2 n_z^{-1}) + b_i}
$$
Neglecting $2$ compared to $n_z$, we find that $N_F = 2/(b_i+b_x)$, which leads to 
$N_F = 2/8=1/4$ and  $N_F=2/12=1/6$ for single and double precision, respectively. 
In the general case, in the condition of $n_z$ large compared to 2, 
$$
N_F =  \frac{2 n_v n_m}{n_m b_x + b_i}
$$ 
The case are interested in is $n_m=n_v=4$, so that
$$
N_F = \frac{8}{ b_x + 1}
$$
which is 8/5 and 8/9 in single and double precision, respectively. 
In single and double precision, we get $N_F=32/36=8/5$ and $N_F=32/68=8/9$, respectively.
The third column of the following table (TABLE ???) is the maximum achievable Gflop rate, assuming 
a maximum memory transfer speed of $150 Gflops$ (see earlier benchmark in this paper). 
(higher speeds can be achieved in practice,  upwards of 190 Gflops (Saule \etal\cite{}), but we use
a benchmark code similar to our current algorithm, without the indirect acessing required for $x$, but keeping the same use of vector registers used in our fastest implementation. (DO WE INCLUDE the CODE?)

### 2013-08-22 tables_and_figures.tex
Two more figures.

\newfig{figures/theoretical_performance.png}{0.7}{Peak performance of SpMV algorithm assuming either 1 or 4 matrices and/or vectors. We used a memory bandwidth of 190 Gbytes/sec (based on best measurements with specialized code) and 150 Gbytes/sec (based on measurements in a code similar to the SpMV kernel, with computations removed.)}{fig:peak_perf}

>>>>

%\newfig{figures/theoretical_performance.png}{0.7}{Peak performance of SpMV algorithm assuming either 1 or 4 matrices and/or vectors. We used a memory bandwidth of 190 Gbytes/sec (based on best measurements with specialized code) and 150 Gbytes/sec (based on measurements in a code similar to the SpMV kernel, with computations removed.)}{fig:peak_perf}

\newfig{figures/gflops_peak.png}{0.7}{Peak performance of SpMV algorithm assuming either 1 or 4 matrices and/or vectors. We used a memory bandwidth of 150 Gbytes/sec (based on measurements in a code similar to the SpMV kernel, with computations removed.)}{fig:gflops_peak_perf}

\newfig{figures/speedup_wrt_base.png}{0.7}{Speedup relative to base case using one matrix and one vector.} {fig:speedkup}
